The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-09-27 manuscript/manuscript.qmd
Add figure showing RO/TA pathways

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
```

@@

TODO: Andrew - image of TA/RO pathways

>>>>

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```

@@

TODO: Andrew - image of TA/RO pathways @fig-ro-ta-pathways

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China, either as formal Registered Organizations (ROs) or by undertaking 
#|   specific Temporary Activities (TAs)"
library(tidygraph)
library(ggraph)

ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming withing approved scope",
    "Submit annual work plans (×2)",
    "Submit annual reports (×2)"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

ta_nodes <- tibble(
  step = c(
    "Find an eligible Chinese partner to file paperwork",
    "Obtain PSU approval",
    "Channel money through partner’s bank",
    "Keep programming withing approved scope",
    "Finish work within a year",
    "Submit final project report"
  ),
  type = "Temporary activities (TA)"
)
ta_edges <- tibble(from = 1:5, to = 2:6)
ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)

combined_graph <- bind_graphs(ro_graph, ta_graph)

ggraph(combined_graph, layout = "tree") +
  geom_node_label(
    aes(x = x, y = y, label = step), 
    size = 2.5, label.r = unit(0, units = "pt")
  ) +
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.step, padding = margin(5, 5, 5, 5, "pt")),
      end_cap = label_rect(node2.step, padding = margin(5, 5, 5, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  facet_nodes(vars(type), scales = "free_x") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    strip.text = element_text(hjust = 0.5)
  )
```
